---
title: "16 Similarity"
author: "Timur Sharifullin"
date: "2023-04-12"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(stringr)
library(ggplot2)
library(lubridate)
library(reshape2)
library(proxy)

knitr::opts_chunk$set(echo = TRUE)
final_df = read.csv("final_df1.csv") 
final_df$X = as.factor(final_df$X)
final_df$album_release_date = as.Date(final_df$album_release_date)
row.names(final_df) = NULL
```

1. *rmsP_median* - the more intense and energetic beat (Rock or Hard Electronic Instrumentals have higher values, classic trap, rnb, voice only audio messages or instrumentals without drums have lower values)
2. *rmsP_std* - the loudness of the harmonic content changes frequently (hyperpop or parts with changing drum patterns have higher values, pop/dance, voice only audio messages or instrumentals without drums (music with stable drum pattern) have lower values)
3. *contrast_median* - simple music (mostly positive) with one or two instruments has higher values of contrast_median, while songs with instrumental overload, complex multi-layered instrumental (in terms of the number of instruments, not in terms of the notes played) have lower values
4. *contrast_std* - the more variability in sound and therefore - more complexity. Songs where many instruments  change each other (very tonally dynamic, do not become a single layer, as in the case of a low contrast_median) have higher values, music with same sounds/instruments all along the whole song typically has lower values 
5. *tonnetz_median* - A higher median value suggests a more complex harmonic structure with more notes in the tonal system. Conversely, a lower median value suggests a simpler harmonic structure with fewer notes in the tonal system. So, songs with higher tonnetz_median would have more rich sound in terms of notes mixing, while songs with lower tonnetz_median would sound less interesting, but more catchy and simpler due to lack of tonal textures.
6. *tonnetz_std* - A higher standard deviation indicate that the song has more complex tonal relationships or a greater variety of musical elements. On the other hand, a lower standard deviation may suggest a simpler or more repetitive tonal structure.
7. *sound_brightness_noisiness* 
8. *laid_back_groovy_lyrical*
9. *quiet_and_melodic*
10. *overall_spectral_Variability*

```{r}
hits = final_df[final_df$X=="hit",c(6,18:23,27:30)]
hits_date = hits$album_release_date
hits = hits %>% select(-album_release_date)

final_df_sim = final_df[,c(18:23,27:30)]
```

## rmsP_median

```{r}
for(g in seq(1,10,1)){
  start_time0 <- Sys.time()
  final_df_sim[,g] = NA
  
  # Loop through each row of final_df_sim
  for(i in seq_len(nrow(final_df_sim))){
    start_time <- Sys.time()
    
    # Create matrix of current row
    current_matrix <- matrix(final_df_audio[i,g])
    # Create a list of song which was released in a period of past year from observed song (if song == 2017 -> year(2017)) 
    
    if(year(final_df$album_release_date[i])==2017){
      days_before_2017 = 365-as.numeric(final_df$album_release_date[i]-as.Date("2017-01-01"))
      observed_hits = (hits_date-final_df$album_release_date[i]) <= 192
    }
    
    else{
      observed_hits = (final_df$album_release_date[i]-hits_date) >= 0 & (final_df$album_release_date[i]-hits_date) <= 365
    }

    # Create matrix of hits in a last year (according to observed song)
    hits_matrix <- matrix(hits[observed_hits,g])
    
    # Calculate distance using proxy package
    d <- proxy::dist(hits_matrix, current_matrix, method="euclidean")
    
    # Get median similarity for g
    final_df_sim[i,g] <- median(d[d!=0])
    
    cat(paste(g,colnames(final_df_sim)[g],"|",
              "Track №",i+1,"| Loop Time:",
              round(as.numeric(Sys.time()- start_time),2), "| Total Time:",
              round(as.numeric(Sys.time()- start_time0),2),"                                         "),
        "\r")
  }
}

```

## Final Table

```{r}
fin_df = final_df[,-c(18:23,27:30)]

fin_df = cbind(fin_df,final_df_sim)

row.names(fin_df) = NULL
head(fin_df)
```

```{r}
write.csv(fin_df, "fin_df_distance_year.csv",row.names = F)
```


