---
title: "22 Hypothesis 3"
author: "Timur Sharifullin"
date: "2023-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(dplyr)
final_df = read.csv("absolute_final_df.csv")
final_df$X = factor(final_df$X, levels = c("none","hit"))

final_df1 = final_df %>% select(X,is_feat,n_feat)

final_df1
```

# Hypothesis 2

The likelihood of the song achieving success (becoming a hit) will increase if the song is labeled as a collaboration between multiple artists, with the names of all performers indicated as the song authors.

# Assumptions Of GLM

## Assumption - The response variable is binary

X - hit/none

## Assumption - Sample size must be sufficiently large

```{r}
final_df333 = final_df1[,c(1,2)]
final_df333$is_feat = as.factor(final_df333$is_feat)

table(final_df333$is_feat,final_df333$X)
```

# GLM

```{r}
hyp1 = glm(X~is_feat,data = final_df333, family = binomial)

summary(hyp1)
```


## Outliers

```{r}
influencePlot(hyp1, col = "red")
outlierTest(hyp1)
```


## Updating the model

```{r}
hyp1fix <- update(hyp1, subset = c(-1,-4,-212,-259, -262))

summary(hyp1fix)
```

```{r}
library(sjPlot)

plot_model(hyp1fix, type = "pred", terms = c("is_feat")) +
  labs(x = "Presence of Guest Performers", y = "Predicted Probability Of Hit")
```

#-------------------------------------------------------------------------

## Assumption - The response variable is binary

X - hit/none

## Assumption - Sample size must be sufficiently large

```{r}
final_df334 = final_df1[,c(1,3)]
table(as.factor(final_df334$n_feat),final_df334$X)
```

```{r}
final_df334 = filter(final_df334, n_feat < 5)

table(as.factor(final_df334$n_feat),final_df334$X)
```

# GLM

```{r}
final_df334$n_feat = as.numeric(final_df334$n_feat)
hyp1_1 = glm(X~n_feat,data = final_df334, family = binomial)

summary(hyp1_1)
```

## Outliers

```{r}
influencePlot(hyp1_1, col = "red")
outlierTest(hyp1_1)
```


## Updating the model

```{r}
hyp1_1fix <- update(hyp1_1, subset = c(-242,-258,-261,-289))

summary(hyp1_1fix)
```

### Predicted Probabilities
```{r}
library(sjPlot)

plot_model(hyp1_1fix, type = "pred", terms = c("n_feat")) + 
  labs(x = "Number of Guest Performers", y = "Predicted Probability Of Hit")
```



