---
title: "22 Hypothesis 3"
author: "Timur Sharifullin"
date: "2023-04-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stringr)
library(dplyr)
final_df = read.csv("fin_df_distance_year.csv")
final_df$X = factor(final_df$X, levels = c("none","hit"))
final_df$artist_name = as.factor(final_df$artist_name) 
final_df1 = final_df[,c(1,3,5,6,16,18)]
final_df1
```


```{r}
final_df1$is_feat = str_detect(final_df1$artists_all,";")
final_df1$n_feat = str_count(final_df1$artists_all,";")
final_df1$statuses = NA
final_df1$min_status = NA
final_df1$max_status = NA

for(i in seq(1,nrow(final_df1),1)){
  if(final_df1$is_feat[i] == T){
    
    final_df1$statuses[i] = paste(final_df1[final_df1$track_id == final_df1$track_id[i],]$hit_n,collapse = ";")
  }
  else{
    final_df1$statuses[i] = final_df1$hit_n[i]
    final_df1$min_status[i] = final_df1$hit_n[i]
    final_df1$max_status[i] = final_df1$hit_n[i]
    }
}


for(i in seq(1,nrow(final_df1),1)){
  final_df1$min_status[i] = min(as.numeric(unlist(str_split(final_df1$statuses[i],";"))))
  final_df1$max_status[i] = max(as.numeric(unlist(str_split(final_df1$statuses[i],";"))))
}
```


## Descriptive Statistics

```{r}
final_df1 = final_df2
```


### Number of feats

```{r}
summary(as.factor(final_df1$n_feat))
```

```{r}
final_df11 = filter(final_df1, n_feat < 4)
summary(as.factor(final_df11$n_feat))

```


### Number of Statuses

```{r}
as.factor(final_df11$min_status) %>% summary()

final_df3 = final_df11 %>% filter(min_status <16)
```

```{r}
as.factor(final_df3$max_status) %>% summary()

final_df4 = final_df3 %>% filter(max_status <16)
```



## Univariate analysis

```{r}
u1 = glm(X~n_feat,data = final_df4, family = binomial)
u2 = glm(X~max_status,data = final_df4, family = binomial)
u3 = glm(X~min_status,data = final_df4, family = binomial)

summary(u1)
summary(u2)
summary(u3)
```

All coefficients are significant

## GLM

```{r}
m_int_max = glm(X ~ n_feat*max_status,
             data = final_df4, family = binomial(link="logit"))

m_int_min = glm(X ~ n_feat*min_status,
             data = final_df4, family = binomial(link="logit"))

m_int_both = glm(X ~ n_feat*min_status + n_feat*max_status,
             data = final_df4, family = binomial(link="logit"))

summary(m_int_max)
summary(m_int_min)
summary(m_int_both)
```

#### Anova

```{r}
anova(m_int_max, m_int_min,m_int_both, test = "Chisq")
```

### Diagnostics

homoscedasticity -  is not the case for binomial

#### Q-Q Plot

```{r}
qq.gam(m_int_both)
```



#### Hosmer and Lemeshow test

```{r}
library(generalhoslem)
logitgof(final_df4$X, fitted(m_int_both), g = 9)
```

The Hosmer-Lemeshow statistic indicates a poor fit due to the significance value = 0.004118. So, probably we need to go for a Generalized Additive Model.


# GAM

```{r}
# With Just n_feat
m_n_feat = gam(X ~ n_feat,
               data = final_df4,
               family = binomial(link="logit"))

# Interaction n_feat*max_status
m_n_feat_max = gam(X ~ n_feat*max_status,
               data = final_df4,
               family = binomial(link="logit"))

# Interaction n_feat*min_status
m_n_feat_min = gam(X ~ n_feat*min_status,
               data = final_df4,
               family = binomial(link="logit"))

# -------------------------------------------

# With Interaction Effect
m_interaction = gam(X ~ n_feat*max_status + n_feat*min_status,
                    data = final_df4,
                    family = binomial(link="logit"))


# GAM with ti interaction effects

gam_interaction_ti =gam(X ~ ti(max_status) + ti(min_status) + 
                       ti(n_feat,max_status) + ti(n_feat,min_status),
                     data = final_df4,
                     family = binomial(link="logit"))
```

```{r}
rsq = c(summary(m_n_feat)$r.sq,
        summary(m_n_feat_max)$r.sq,
        summary(m_n_feat_min)$r.sq,
        summary(m_interaction)$r.sq,
        summary(gam_interaction_ti)$r.sq)

models = c("m_n_feat",
           "m_n_feat_max",
           "m_n_feat_min",
           "m_interaction",
           "gam_interaction_ti")

data.frame(models,rsq) %>% arrange(-rsq)
```

gam_interaction_ti is the best model according to R2

```{r}
ubre = c(
        summary(gam_max)$sp.criterion,
        summary(gam_min)$sp.criterion,
        summary(gam_both)$sp.criterion,
        summary(gam_interaction)$sp.criterion,
        summary(gam_interaction_ti)$sp.criterion)

models = c(
           "gam_max",
           "gam_min",
           "gam_both",
           "gam_interaction",
           "gam_interaction_ti")

data.frame(models,ubre) %>% arrange(ubre)
```

"Notice that UBRE - Un-Biased Risk Estimator - is effectively just AIC rescaled, but is only used when s is known."

gam_interaction_ti has the smallest UBRE.


```{r}
anova(m_n_feat, #1
      m_n_feat_max, #2
      m_n_feat_min, #3
      m_linear, #4
      m_interaction, #5
      gam_max, #6
      gam_min, #7
      gam_both, #8
      gam_interaction, #9
      gam_interaction_ti, #10
      test = "Chisq")
```
By ANOVA Test, gam_interaction_ti is the best model. 

## GAM Diagnostics
```{r}
gam.check(gam_interaction_ti)
```

ti(n_feat,max_status) - k' and edf is not close, so k is not too low
ti(min_status) - has close values of k' and edf, so, the k should be changed

```{r}
# GAM with ti interaction effects

gam_interaction_ti1 =gam(X ~ ti(max_status, k = 12) + ti(n_feat, k = 6) + ti(min_status, k = 13) + 
                       ti(n_feat,max_status) + ti(n_feat,min_status),
                     data = final_df1,
                     family = binomial(link="logit"))

gam.check(gam_interaction_ti1)
```

Now it is looking okay. 

```{r}
summary(gam_interaction_ti1)
```
The edf is a summary statistic of GAM and it reflects the degree of non-linearity of a curve (Wood 2006). An edf equal to 1 is equivalent to a linear relationship, 1 < edf ≤ 2 is considered a weakly non-linear relationship, and edf > 2 implies a highly non-linear relationship

```{r}
plot(ggeffects::ggpredict(gam_interaction_ti1))
plot(gam_interaction_ti1)
```

All of the coefficients are 
The Hypothesis is true.

