---
title: "Final_Full_GAM2"
author: "Timur Sharifullin"
date: "2023-05-11"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(gridExtra)
library(grid)
library(mgcv)
library(sjPlot)
final_df = read.csv("Clean_Dataset.csv")
```

```{r}

final_df$higher_guest = factor(final_df$higher_guest,labels = c("No","Yes"))

final_df1 = final_df %>% dplyr::select(-"artist_name",-"status_guest",-"n_feat","is_feat")

final_df1$Song_Success = factor(final_df1$Song_Success, levels = c("none","hit"), labels=c("Non-Hit","Hit"))


final_df2 = final_df1[final_df1$hit_n < 17,]

final_df2
```

# Descriptive Statistics
```{r}
library(table1)
library(flextable)
label(final_df2$higher_guest) = "Presence of Guest Artists with Higher Status"

final_df2$hit_n = as.factor(final_df2$hit_n)
label(final_df2$hit_n) = "Number of Previous Hits"

label(final_df2$Drums_Energy) = "Drums Energy"
label(final_df2$Drums_Complexity) = "Drums Complexity"
label(final_df2$Variety_of_musical_instruments) = "Variety of Musical Instruments"
label(final_df2$Harmonic_Richness) = "Harmonic Richness"
label(final_df2$Emotional_Intensity) = "Emotional Intensity"
label(final_df2$Mixing_Quality) = "Mixing Quality"

final_model_desc = table1(~ as.factor(hit_n) + higher_guest +
                            Drums_Energy + Drums_Complexity + Variety_of_musical_instruments + Harmonic_Richness +
                            Emotional_Intensity| Song_Success, data=final_df2)
final_model_desc

final_df2$hit_n = as.numeric(final_df2$hit_n)-1

#t1flex(final_model_desc) %>% 
#  save_as_docx(path="final_model_desc.docx")
```

# Base Model
```{r}
gam_full1 = gam(Song_Success ~
              hit_n +
              higher_guest +
              s(Drums_Energy) +
              s(Drums_Complexity) +
              s(Variety_of_musical_instruments) +
              s(Harmonic_Richness) +
              s(Emotional_Intensity),
            data = final_df2,
            family = binomial(link="logit"),
            method = "REML")
summary(gam_full1)
```

```{r}
k.check(gam_full1)
```


# Outliers

```{r}
# initial model to find k-value
# - gam_full1


# model without penalization with ceiling(k)+1
gam_7_1 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                s(Drums_Energy, k = ceiling(k.check(gam_full1)[1,2])+1, fx = TRUE) +
                s(Drums_Complexity, k = ceiling(k.check(gam_full1)[2,2])+1, fx = TRUE) +
                s(Variety_of_musical_instruments, k = ceiling(k.check(gam_full1)[3,2])+1, fx = TRUE) +
                s(Harmonic_Richness, k = ceiling(k.check(gam_full1)[4,2])+1, fx = TRUE) +
                s(Emotional_Intensity, k = ceiling(k.check(gam_full1)[5,2])+1, fx = TRUE),
            data = final_df2,
            family = binomial(link="logit"),
            method = "REML")

# Influential values (Outliers)
inf = influence.gam(gam_7_1)
cook = cooks.distance(gam_7_1)
final_df2$inf = inf
final_df2$cook = cook
par(mfrow=c(1,2))
plot(inf,ylab = "Hat-value")
abline(h=0.0075, col="red")
plot(cook,ylab = "Cook's  Distance")
abline(h=0.001, col="red")

# New Dataset
final_df3 = subset(final_df2, inf < 0.0075 & cook <0.001)

# Final Model
gam_7_final = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                s(Drums_Energy) +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final)
```

```{r}
nrow(final_df3)-nrow(final_df2)
```


```{r}
# Base model
gam_7_final
```


```{r}
gam_7_energy = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                s(Drums_Energy) +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                Emotional_Intensity,
            data = final_df3,
            family = binomial,
            method = "REML")

AIC(gam_7_final,gam_7_energy)
anova(gam_7_final,gam_7_energy,test="Chisq") %>% as.data.frame()
```

# Model without interactive effects

```{r}
gam_7_final_f = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_f)
```

# Predicted Probs
```{r}
library(ggeffects)
pred = ggpredict(gam_7_final_f)

p1 = plot(pred)[[1]] +
  labs(title = NULL, x = "Number of Previous Hits\n",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

p2 = plot(pred)[[2]] +
  labs(title = NULL,x = "Presence of Guest Artists\nwith Higher Status",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

p3 = plot(pred)[[3]] +
  labs(title = NULL,x = "Dissimilarity by\nDrums Energy",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

p4 = plot(pred)[[4]] +
  labs(title = NULL,x = "Dissimilarity by\nDrums Complexity",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

p5 = plot(pred)[[5]] +
  labs(title = NULL,x = "Dissimilarity by\nVariety of Musical Instruments",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

p6 = plot(pred)[[6]] +
  labs(title = NULL,x = "Dissimilarity by\nHarmonic Richness",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

p7 = plot(pred)[[7]] +
  labs(title = NULL,x = "Dissimilarity by\nEmotional Intensity",y = NULL) +
  scale_y_continuous(breaks = seq(0,1,0.1)) +
  coord_cartesian(ylim = c(0,0.6))

combined_plot = grid.arrange(p3,p4,p5,p6,p7, #p1,p2, 
                             left = "Predicted Probability of Hit",
                             nrow=2, ncol=3)

# -----------------------------------------

datka = ggpredict(u5) %>% as.data.frame()

ggpredict(u5) 
summary(u5)
```




# Model with Interactive Effects

```{r}
gam_7_final_it = gam(Song_Success ~ 
                hit_n +
                higher_guest*hit_n +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity,by = hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_it)
```

```{r}
AIC(gam_7_final_f,gam_7_final_it)
anova(gam_7_final_f,gam_7_final_it, test = "Chisq")
```


## hit_n

```{r}
hit1 = gam(Song_Success ~ 
                hit_n +
                higher_guest*hit_n +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

hit2 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity, by = hit_n) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

hit3 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments, by = hit_n) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

hit4 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness, by = hit_n) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

hit5 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity,by=hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")
summary(hit5)
```


```{r}
plot_hit1 = plot_model(hit1,
           type = "pred",
           terms = c("higher_guest","hit_n[0,1,5,12,16]"),
           title = NULL,
           legend.title = "Number of previous hits") + labs(x="Guest with higher N of hits",y=NULL,title=NULL)

plot_hit2 = plot_model(hit2,
           type = "pred",
           terms = c("Drums_Complexity","hit_n[0,1,5,12,16]"),
           title = NULL) + labs(x = "Dissimilarity by\nDrums Complexity",y=NULL,title=NULL) + theme(legend.position = "none")

plot_hit3 = plot_model(hit3,
           type = "pred",
           terms = c("Variety_of_musical_instruments","hit_n[0,1,5,12,16]"),
           title = NULL) + labs(x="Dissimilarity by\nVariety of instruments",y=NULL,title=NULL) + theme(legend.position = "none")

plot_hit4 = plot_model(hit4,
           type = "pred",
           terms = c("Harmonic_Richness","hit_n[0,1,5,12,16]"),
           title = NULL) + labs(x="Dissimilarity by\nHarmonic Richness",y=NULL,title=NULL) + theme(legend.position = "none")

plot_hit5 = plot_model(hit5,
           type = "pred",
           terms = c("Emotional_Intensity","hit_n[0,1,5,12,16]"),
           title = NULL) + labs(x="Dissimilarity by\nEmotional Intensity",y=NULL,title=NULL) + theme(legend.position = "none")

plot = plot_hit1
# get tabular interpretation of plot
plot_table <- ggplot_gtable(ggplot_build(plot)) 
#  Mark only legend in plot
legend_plot <- which(sapply(plot_table$grobs, function(x) x$name) == "guide-box") 
# extract legend
legend <- plot_table$grobs[[legend_plot]]

grid.arrange(plot_hit2,plot_hit3,plot_hit4,plot_hit5,plot_hit1 + theme(legend.position = "none"),
                             legend,
                             left = "Predicted Probability of Hit",
                             nrow=2, ncol=3)
```


# higher_guest
```{r}
higher2 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity, higher_guest, bs="fs") +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

higher3 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments, higher_guest, bs="fs") +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

higher4 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness, higher_guest, bs="fs") +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

higher5 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                Drums_Energy +
                s(Drums_Complexity) +
                s(Variety_of_musical_instruments) +
                s(Harmonic_Richness) +
                s(Emotional_Intensity, higher_guest, bs="fs"),
            data = final_df3,
            family = binomial,
            method = "REML")
```

```{r}
plot_higher2 = plot_model(higher2,
           type = "pred",
           terms = c("Drums_Complexity","higher_guest"),
           title = NULL,
           legend.title = "Guest with higher N of hits") +
  labs(x = "Dissimilarity by\nDrums Complexity",y=NULL,title=NULL) +
  scale_color_manual(values = c("red","darkorange")) +
  scale_fill_manual(values = c("red","darkorange"))
  

plot_higher3 = plot_model(higher3,
           type = "pred",
           terms = c("Variety_of_musical_instruments","higher_guest"),
           title = NULL) +
  labs(x="Dissimilarity by\nVariety of instruments",y=NULL,title=NULL) +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red","darkorange")) +
  scale_fill_manual(values = c("red","darkorange"))

plot_higher4 = plot_model(higher4,
           type = "pred",
           terms = c("Harmonic_Richness","higher_guest"),
           title = NULL) +
  labs(x="Dissimilarity by\nHarmonic Richness",y=NULL,title=NULL) +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red","darkorange")) +
  scale_fill_manual(values = c("red","darkorange"))

plot_higher5 = plot_model(higher5,
                          type = "pred",
                          terms = c("Emotional_Intensity","higher_guest"),
                          title = NULL) + 
  labs(x="Dissimilarity by\nEmotional Intensity",y=NULL,title=NULL) + 
  theme(legend.position = "none") +
  scale_color_manual(values = c("red","darkorange")) +
  scale_fill_manual(values = c("red","darkorange"))

plot = plot_higher2
# get tabular interpretation of plot
plot_table <- ggplot_gtable(ggplot_build(plot)) 
#  Mark only legend in plot
legend_plot <- which(sapply(plot_table$grobs, function(x) x$name) == "guide-box") 
# extract legend
legend <- plot_table$grobs[[legend_plot]]

grid.arrange(plot_higher2 + theme(legend.position = "none"),
             plot_higher3,plot_higher4,plot_higher5, legend,
             left = "Predicted Probability of Hit",
             nrow=2, ncol=3)
```




```{r}
gam_7_final_ti = gam(Song_Success ~ 
                  hit_n +
                  higher_guest +
                  Drums_Energy +
                  Drums_Complexity +
                  Variety_of_musical_instruments +
                  Emotional_Intensity +
                  s(Harmonic_Richness) +
                  s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_ti)

AIC(gam_7_final_f,gam_7_final_ti)
anova(gam_7_final_f,gam_7_final_ti, test = "Chisq")
```

higher_guest*Drums_Energy - no sign
higher_guest*Drums_Complexity - sign
higher_guest*Variety_of_musical_instruments - non-sign
higher_guest*Harmonic_Richness - non-sign
higher_guest*Emotional_Intensity - sign but worsen the model

```{r}
gam_7_final_ti = gam(Song_Success ~ 
                  hit_n +
                  higher_guest +
                  Drums_Energy +
                  Drums_Complexity +
                  Variety_of_musical_instruments +
                  s(Harmonic_Richness) +
                  ti(Drums_Energy,Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_ti)

AIC(gam_7_final_f,gam_7_final_ti)
anova(gam_7_final_f,gam_7_final_ti, test = "Chisq")
```

Drums_Energy*Drums_Complexity - non-sign (0.136642)
Drums_Energy*Variety_of_musical_instruments - non-sign (0.2787)
ti(Drums_Energy,Harmonic_Richness) - non-sign (0.115)
ti(Drums_Energy,Emotional_Intensity) - sign (0.00198), but worsen the model (anova: 12800     9355.9 -2.5336  -44.968 4.418e-10 ***, aic:15.19727	9386.327)

```{r}
gam_7_final_ti = gam(Song_Success ~ 
                  hit_n +
                  higher_guest +
                  Drums_Energy +
                  Drums_Complexity +
                  Variety_of_musical_instruments +
                  s(Harmonic_Richness) +
                  ti(Drums_Complexity,Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_ti)

AIC(gam_7_final_f,gam_7_final_ti)
anova(gam_7_final_f,gam_7_final_ti, test = "Chisq")
```

Drums_Complexity*Variety_of_musical_instruments - non-sign
Drums_Complexity*Harmonic_Richness - non-sign (0.654)
ti(Drums_Complexity,Emotional_Intensity) - sign (7.33e-08), worsen the model fit not significantly (anova: 12794     9322.9 3.2179   -11.96, aic: 20.05922	9363.043)

```{r}
gam_7_final_ti = gam(Song_Success ~ 
                  hit_n +
                  higher_guest +
                  Drums_Energy +
                  Drums_Complexity +
                  Variety_of_musical_instruments +
                  s(Harmonic_Richness) +
                  ti(Variety_of_musical_instruments,Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_ti)

AIC(gam_7_final_f,gam_7_final_ti)
anova(gam_7_final_f,gam_7_final_ti, test = "Chisq")
```

ti(Variety_of_musical_instruments,Harmonic_Richness) - non-sign (0.224)
ti(Variety_of_musical_instruments,Emotional_Intensity) - non-sign (0.84868)

```{r}
gam_7_final_ti = gam(Song_Success ~ 
                  hit_n +
                  higher_guest +
                  Drums_Energy +
                  Drums_Complexity +
                  Variety_of_musical_instruments +
                  s(Harmonic_Richness) +
                  ti(Harmonic_Richness,Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_ti)

AIC(gam_7_final_f,gam_7_final_ti)
anova(gam_7_final_f,gam_7_final_ti, test = "Chisq")
```

ti(Harmonic_Richness,Emotional_Intensity) - non-significant (0.17118)


# Final Final Model

```{r}
m1 = gam(Song_Success ~ 
                hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")

m2 = gam(Song_Success ~ 
           hit_n +
           higher_guest,
            data = final_df3,
            family = binomial,
            method = "REML")

m2_int_hit_n = gam(Song_Success ~ 
           hit_n +
           higher_guest +
           higher_guest*hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")
AIC(m1,m2,m2_int_hit_n)
anova(m1,m2,m2_int_hit_n,test="Chisq")
```

Interaction Term higher_guest*hit_n is important

```{r}
summary(m2_int_hit_n)
```

Interaction Term higher_guest*hit_n is significant

```{r}
m1 = gam(Song_Success ~ 
            Drums_Energy,
            data = final_df3,
            family = binomial,
            method = "REML")

m1s = gam(Song_Success ~ hit_n +
            s(Drums_Energy),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n_s = gam(Song_Success ~ 
           s(Drums_Energy,hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n = gam(Song_Success ~ 
           Drums_Energy*hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_higher = gam(Song_Success ~ 
           Drums_Energy*higher_guest,
            data = final_df3,
            family = binomial,
            method = "REML")

AIC(m1,m1_int_hit_n,m1_int_higher)
anova(m1,m1_int_hit_n,m1_int_higher,test="Chisq")
```

Drums_Energy*hit_n is important (m1_int_hit_n)

```{r}
summary(m1_int_hit_n)
summary(m1_int_hit_n_s)
summary(m1_int_higher)
```

Drums_Energy*hit_n is not significant
Drums_Energy*higher_guestYes is not significant
s(Drums_Energy,hit_n) is significant

```{r}
plot_model(m1s,type="pred", terms = c("Drums_Energy", "hit_n[0,5,12,16]"))
```

```{r}
m1 = gam(Song_Success ~ 
            Drums_Complexity,
            data = final_df3,
            family = binomial,
            method = "REML")

m1s = gam(Song_Success ~ hit_n +
            s(Drums_Complexity),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n_s = gam(Song_Success ~ 
           s(Drums_Complexity,hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n = gam(Song_Success ~ 
           Drums_Complexity*hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_higher = gam(Song_Success ~ 
           Drums_Complexity*higher_guest,
            data = final_df3,
            family = binomial,
            method = "REML")

AIC(m1,m1_int_hit_n,m1_int_higher)
anova(m1,m1_int_hit_n,m1_int_higher,test="Chisq")
```

Drums_Complexity*hit_n is important (m1_int_hit_n)

```{r}
summary(m1_int_hit_n)
summary(m1_int_higher)
summary(m1_int_hit_n_s)
```

Drums_Complexity*hit_n is not significant
Drums_Complexity*higher_guestYes is significant
s(Drums_Complexity,hit_n) is significant

```{r}
plot_model(m1s,type="pred", terms = c("Drums_Complexity", "hit_n[0,5,12,16]"))
```


```{r}
m1 = gam(Song_Success ~ 
            Variety_of_musical_instruments,
            data = final_df3,
            family = binomial,
            method = "REML")

m1s = gam(Song_Success ~ hit_n +
            s(Variety_of_musical_instruments),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n = gam(Song_Success ~ 
           Variety_of_musical_instruments*hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n_s = gam(Song_Success ~ 
           s(Variety_of_musical_instruments,hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_higher = gam(Song_Success ~ 
           Variety_of_musical_instruments*higher_guest,
            data = final_df3,
            family = binomial,
            method = "REML")

AIC(m1,m1_int_hit_n,m1_int_higher)
anova(m1,m1_int_hit_n,m1_int_higher,test="Chisq")
```

s(Variety_of_musical_instruments,hit_n) is important
Variety_of_musical_instruments*hit_n is important

```{r}
summary(m1_int_hit_n)
summary(m1_int_higher)
summary(m1_int_hit_n_s)
```

s(Variety_of_musical_instruments,hit_n) significant

```{r}
plot_model(m1s,type="pred", terms = c("Variety_of_musical_instruments", "hit_n[0,5,12,16]"))
```


```{r}
m1 = gam(Song_Success ~ 
            Harmonic_Richness,
            data = final_df3,
            family = binomial,
            method = "REML")

m1s = gam(Song_Success ~ hit_n +
            s(Harmonic_Richness),
            data = final_df3,
            family = binomial,
            method = "REML")

m1s_int_hit_n = gam(Song_Success ~ 
            s(Harmonic_Richness,hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n = gam(Song_Success ~ 
           Harmonic_Richness*hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_higher = gam(Song_Success ~ 
           Harmonic_Richness*higher_guest,
            data = final_df3,
            family = binomial,
            method = "REML")


AIC(m1,m1s,m1s_int_hit_n,m1_int_hit_n,m1_int_higher)
anova(m1,m1s,m1s_int_hit_n,m1_int_hit_n,m1_int_higher,test="Chisq")
```

s(Harmonic_Richness, hit_n) - interaction term is important

```{r}
summary(m1s_int_hit_n)
summary(m1_int_hit_n)
summary(m1_int_higher)
```
Harmonic_Richness*hit_n is significant
s(Harmonic_Richness,hit_n) is significant
Harmonic_Richness*higher_guestYes is not

```{r}
plot_model(m1s,type="pred", terms = c("Harmonic_Richness", "hit_n[0,5,12,16]"))
```



```{r}
m1 = gam(Song_Success ~ 
            Emotional_Intensity,
            data = final_df3,
            family = binomial,
            method = "REML")

m1s = gam(Song_Success ~ hit_n +
            s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

m1s_int_hit_n = gam(Song_Success ~ 
            s(Emotional_Intensity,hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_hit_n = gam(Song_Success ~ 
           Emotional_Intensity*hit_n,
            data = final_df3,
            family = binomial,
            method = "REML")

m1_int_higher = gam(Song_Success ~ 
           Emotional_Intensity*higher_guest,
            data = final_df3,
            family = binomial,
            method = "REML")


AIC(m1,m1s,m1s_int_hit_n,m1_int_hit_n,m1_int_higher)
anova(m1,m1s,m1s_int_hit_n,m1_int_hit_n,m1_int_higher,test="Chisq")
```

s(Emotional_Intensity,hit_n) is important

```{r}
summary(m1s_int_hit_n)
summary(m1_int_hit_n)
summary(m1_int_higher)
```

s(Emotional_Intensity,hit_n) is significant
Emotional_Intensity*hit_n is not
Emotional_Intensity*higher_guestYes is significant

```{r}
plot_model(m1s,type="pred", terms = c("Emotional_Intensity", "hit_n[0,5,12,16]"))
vis.gam(m1s_int_hit_n)
```

# Additional

```{r}
m_aaa = gam(Song_Success ~ 
                higher_guest*hit_n +
                s(Drums_Energy,hit_n) +
                s(Drums_Complexity,hit_n) +
                s(Variety_of_musical_instruments,hit_n) +
                s(Harmonic_Richness,hit_n) +
                s(Emotional_Intensity,hit_n),
            data = final_df3,
            family = binomial,
            method = "REML")

summary(m_aaa)
```




```{r}
m10 = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                higher_guest*hit_n +
                Drums_Energy +
                Drums_Complexity +
                higher_guest*Drums_Complexity +
                Variety_of_musical_instruments +
                s(Harmonic_Richness) +
                s(Emotional_Intensity),
            data = final_df3,
            family = binomial,
            method = "REML")

gam_7_final_final = gam(Song_Success ~ 
                hit_n +
                higher_guest +
                higher_guest*hit_n +
                Drums_Energy +
                Drums_Complexity +
                higher_guest*Drums_Complexity +
                Variety_of_musical_instruments +
                s(Harmonic_Richness) +
                higher_guest*Emotional_Intensity,
            data = final_df3,
            family = binomial,
            method = "REML")

summary(gam_7_final_final)
```

```{r}

```


```{r}
plot_model(gam_7_final_final, pred.type = )
```

# No Concurvity

```{r}
concurvity(gam_7_final,full=TRUE)%>% as.data.frame() %>% round(3)
```

# No multicollinearity

```{r}
library(corrtable)
df_cor = final_df3[,c(4:7,9,11,13)]
df_cor$higher_guest = as.numeric(df_cor$higher_guest)-1

correlation_matrix(df = df_cor,
                        type = "spearman",
                        use = "lower",
                        show_significance = TRUE)

save_correlation_matrix(df = df_cor,
                        type = "spearman",
                        use = "lower",
                        show_significance = TRUE,
                        filename = "cor_table_audio.csv")
```

# k check

```{r}
gam.check(gam_7_final_f)
```




