---
title: "21 Hypothesis 2_with_log_reg"
author: "Timur Sharifullin"
date: "2023-04-26"
output: html_document
---

```{r}
library(ggplot2)
library(dplyr)
library(tidyverse)
library(gridExtra)
library(grid)
library(mgcv)
library(ggeffects)
final_df = read.csv("Clean_Dataset.csv")
```


*Hypothesis 3.*
The relationship between the sound originality and the likelihood of the song achieving success (becoming a hit) is inverted U-shaped. As the degree of sound originality of the song increases, the likelihood of the song becoming a hit will increase up to a certain point. However, if the degree of sound originality exceeds a certain point, this will lead to a decrease in likelihood of the song becoming a hit.


```{r}
final_df1 = final_df %>% dplyr::select(-"artist_name",-"album_release_date",-"hit_n",-"is_feat",-"n_feat")
final_df1$Song_Success = factor(final_df1$Song_Success, levels = c("none","hit"))

final_df1 = final_df1[!duplicated(final_df1[,1]),] %>% dplyr::select(-track_id)

head(final_df1)
```

# Descriptive Stats
```{r}
p1 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[,2],fill = Song_Success), bins=1000) +
      labs(x = "Drums Energy",fill="Song Success") +
      scale_fill_discrete(labels = c("Non-Hit","Hit")) +
      theme(legend.position = "bottom",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p2 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[,3],fill = Song_Success), bins=1000) +
      labs(x = "Drums Complexity") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p3 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[,4],fill = Song_Success), bins=1000) +
      labs(x = "Variety of Musical Instruments") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p4 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[, 5],fill = Song_Success), bins=1000) +
      labs(x = "Harmonic Richness") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p5 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[,6],fill = Song_Success), bins=1000) +
      labs(x = "Emotional Intensity") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p6 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[,7],fill = Song_Success), bins=1000) +
      labs(x = "Mixing Quality") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p7 = ggplot(data = final_df1) +
      geom_histogram(aes(x = final_df1[,8],fill = Song_Success), bins=1000) +
      labs(x = "Mixing Character") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())
plot = p1
# get tabular interpretation of plot
plot_table <- ggplot_gtable(ggplot_build(plot)) 
#  Mark only legend in plot
legend_plot <- which(sapply(plot_table$grobs, function(x) x$name) == "guide-box") 
# extract legend
legend <- plot_table$grobs[[legend_plot]]

combined_plot = grid.arrange(p1 + theme(legend.position="none"),p2,p3,
                             p4,p5,p6,p7,legend,
                             left = "Count", bottom = "Audio Feature Dissimilarity")

```


```{r}
library(car)
vec = final_df1$Drums_Energy %in% boxplot.stats(final_df1$Drums_Energy)$out
d_energy = final_df1[!vec,]

vec = final_df1$Drums_Complexity %in% boxplot.stats(final_df1$Drums_Complexity)$out
d_complex = final_df1[!vec,]

vec = final_df1$Variety_of_musical_instruments %in% boxplot.stats(final_df1$Variety_of_musical_instruments)$out
d_variety = final_df1[!vec,]

vec = final_df1$Harmonic_Richness %in% boxplot.stats(final_df1$Harmonic_Richness)$out
d_h_rich = final_df1[!vec,]

vec = final_df1$Emotional_Intensity %in% boxplot.stats(final_df1$Emotional_Intensity)$out
d_emot = final_df1[!vec,]

vec = final_df1$Mixing_Quality %in% boxplot.stats(final_df1$Mixing_Quality)$out
d_m_qual = final_df1[!vec,]

vec = final_df1$Mixing_Character %in% boxplot.stats(final_df1$Mixing_Character)$out
d_m_char = final_df1[!vec,]
```

# Descriptive Statistics 2

```{r}
p1 = ggplot(data = d_energy) +
      geom_histogram(aes(x = d_energy$Drums_Energy,fill = Song_Success), bins=1000) +
      labs(x = "Drums Energy",fill="Song Success") +
      scale_fill_discrete(labels = c("Non-Hit","Hit")) +
      theme(legend.position = "bottom",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p2 = ggplot(data = d_complex) +
      geom_histogram(aes(x = d_complex$Drums_Complexity,fill = Song_Success), bins=1000) +
      labs(x = "Drums Complexity") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p3 = ggplot(data = d_variety) +
      geom_histogram(aes(x = d_variety$Variety_of_musical_instruments,fill = Song_Success), bins=1000) +
      labs(x = "Variety of Musical Instruments") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p4 = ggplot(data = d_h_rich) +
      geom_histogram(aes(x = d_h_rich$Harmonic_Richness,fill = Song_Success), bins=1000) +
      labs(x = "Harmonic Richness") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p5 = ggplot(data = d_emot) +
      geom_histogram(aes(x = d_emot$Mixing_Quality,fill = Song_Success), bins=1000) +
      labs(x = "Emotional Intensity") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p6 = ggplot(data = d_m_qual) +
      geom_histogram(aes(x = d_m_qual$Mixing_Quality,fill = Song_Success), bins=1000) +
      labs(x = "Mixing Quality") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

p7 = ggplot(data = d_m_char) +
      geom_histogram(aes(x = d_m_char$Mixing_Character,fill = Song_Success), bins=1000) +
      labs(x = "Mixing Character") +
      theme(legend.position = "none",
            axis.title.x = element_text(size = 8),
            axis.title.y = element_blank())

plot = p1
# get tabular interpretation of plot
plot_table <- ggplot_gtable(ggplot_build(plot)) 
#  Mark only legend in plot
legend_plot <- which(sapply(plot_table$grobs, function(x) x$name) == "guide-box") 
# extract legend
legend <- plot_table$grobs[[legend_plot]]

combined_plot = grid.arrange(p1 + theme(legend.position="none"),p2,p3,
                             p4,p5,p6,p7,legend,
                             left = "Count", bottom = "Audio Feature Dissimilarity")
```


# Univariate models
```{r}
u1 = gam(Song_Success~s(Drums_Energy),data = d_energy, family = binomial,method = "REML")
u2 = gam(Song_Success~s(Drums_Complexity),data = d_complex,family = binomial,method = "REML")
u3 = gam(Song_Success~s(Variety_of_musical_instruments),data = d_variety, family = binomial,method = "REML")
u4 = gam(Song_Success~s(Harmonic_Richness),data = d_h_rich, family = binomial,method = "REML")
u5 = gam(Song_Success~s(Emotional_Intensity),data = d_emot, family = binomial,method = "REML")
u6 = gam(Song_Success~s(Mixing_Quality),data = d_m_qual, family = binomial,method = "REML")
u7 = gam(Song_Success~s(Mixing_Character),data = d_m_char, family = binomial,method = "REML")

summary(u1)$s.table
summary(u2)$s.table
summary(u3)$s.table
summary(u4)$s.table
summary(u5)$s.table
summary(u6)$s.table
summary(u7)$s.table
```

0.0002500438 - sign
0.005381333 - sign
0.0000771487 - sign
0.02512154 - sign
0.001158294 - sign
0.2851457 - no
0.5519767 -  no


```{r}
l1 = gam(Song_Success~Drums_Energy,data = d_energy, family = binomial,method = "REML")
l2 = gam(Song_Success~Drums_Complexity,data = d_complex,family = binomial,method = "REML")
l3 = gam(Song_Success~Variety_of_musical_instruments,data = d_variety, family = binomial,method = "REML")
l4 = gam(Song_Success~Harmonic_Richness,data = d_h_rich, family = binomial,method = "REML")
l5 = gam(Song_Success~Emotional_Intensity,data = d_emot, family = binomial,method = "REML")
l6 = gam(Song_Success~Mixing_Quality,data = d_m_qual, family = binomial,method = "REML")
l7 = gam(Song_Success~Mixing_Character,data = d_m_char, family = binomial,method = "REML")

summary(l7)
```

```{r}
# Predict the probability (p) of song success
probabilities <- predict(l1, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_energy) %>% dplyr::select(Drums_Energy)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p1 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) +
  theme_bw() +
  labs(y = "Dissimilarity by\nDrums Energy",x=NULL) +
  coord_flip()

# ------------------------------------------------------------------------
  
# Predict the probability (p) of song success
probabilities <- predict(l2, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_complex) %>% dplyr::select(Drums_Complexity)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p2 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) + 
  theme_bw() +
  labs(y = "Dissimilarity by\nDrums Complexity",x=NULL) +
  coord_flip()

# ------------------------------------------------------------------------
  
# Predict the probability (p) of song success
probabilities <- predict(l3, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_variety) %>% dplyr::select(Variety_of_musical_instruments)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p3 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) + 
  theme_bw() +
  labs(y = "Dissimilarity by\nVariety of Musical Instruments",x=NULL) +
  coord_flip()

# ------------------------------------------------------------------------
  
# Predict the probability (p) of song success
probabilities <- predict(l4, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_h_rich) %>% dplyr::select(Harmonic_Richness)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p4 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) + 
  theme_bw() +
  labs(y = "Dissimilarity by\nHarmonic Richness",x=NULL) +
  coord_flip()

# ------------------------------------------------------------------------
  
# Predict the probability (p) of song success
probabilities <- predict(l5, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_emot) %>% dplyr::select(Emotional_Intensity)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p5 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) + 
  theme_bw() +
  labs(y = "Dissimilarity by\nEmotional Intensity",x=NULL) +
  coord_flip()

# ------------------------------------------------------------------------
  
# Predict the probability (p) of song success
probabilities <- predict(l6, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_m_qual) %>% dplyr::select(Mixing_Quality)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p6 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) + 
  theme_bw() +
  labs(y = "Dissimilarity by\nMixing Quality",x=NULL) +
  coord_flip()

# ------------------------------------------------------------------------
  
# Predict the probability (p) of song success
probabilities <- predict(l7, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(d_m_char) %>% dplyr::select(Mixing_Character)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

p7 = ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 0.05, alpha = 0.8) +
  theme_bw() +
  labs(y = "Dissimilarity by\nMixing Character",x=NULL) +
  coord_flip()

combined_plot = grid.arrange(p1,p2,p3,p4,
                             p5,p6,p7,
                             left = "Logit of the Song Success",
                             nrow=2, ncol=4)
```


## Checking k basis

```{r}
k.check(u7)
#gam.check(u1)
```

All k basis are not too low


```{r}
AIC(u1,l1)
AIC(u2,l2)
AIC(u3,l3)
AIC(u4,l4)
AIC(u5,l5)
AIC(u6,l6)
AIC(u7,l7)
```

Drums_Energy - Similar
Drums_Complexity - Similar(closer to linear)
Variety_of_musical_instruments - similar according to AIC (the smooth term will be used)
Harmonic_Richness - Smooth
Emotional_Intensity - Smooth
Mixing_Quality - Linear
Mixing_Character - Linear

```{r}
anova.gam(u1,l1, test = "Chisq")
anova.gam(u2,l2, test = "Chisq")
anova.gam(u3,l3, test = "Chisq")
anova.gam(u4,l4, test = "Chisq")
anova.gam(u5,l5, test = "Chisq")
anova.gam(u6,l6, test = "Chisq")
anova.gam(u7,l7, test = "Chisq")
```

Drums_Energy - Smooth
Drums_Complexity - Smooth
Variety_of_musical_instruments - Smooth
Harmonic_Richness - Smooth (sign)
Emotional_Intensity - Smooth (sign)
Mixing_Quality - Smooth
Mixing_Character - Smooth


```{r}
model_n = u5
summary(model_n)
var_name = row.names(as.data.frame(model_n$coefficients[2])) %>%
              str_sub(start = 3, end = -4) %>%
              str_replace_all(pattern = "_", " ")
line_y = as.numeric(model_n$coefficients[1]) %>% plogis()

plot(ggpredict(model_n))[[1]] +
  labs(title = "Predicted Probabilities of Song Success",
       x = paste("Dissimiliarity by", var_name),
       y = "Predicted Probability of Hit") +
  scale_x_continuous(breaks = seq(0,10,0.25)) +
  scale_y_continuous(breaks = seq(0,1,0.01))

# -----------------------------------------

datka = ggpredict(u5) %>% as.data.frame()

ggpredict(u5) 
summary(u5)
```

Drums_Energy - linear down
Drums_Complexity - linear down
Variety_of_musical_instruments - linear down
Harmonic_Richness - inv u-shaped
Emotional_Intensity - inv u-shaped


```{r}
gam_full = gam(Song_Success~
                 Drums_Energy +
                 s(Drums_Complexity) +
                 s(Variety_of_musical_instruments) +
                 s(Harmonic_Richness) +
                 s(Emotional_Intensity)+
                 s(Mixing_Quality),
               data = final_df1,
               family = binomial,
               method = "REML",
               method.args = list(control = list(type =  "huber")))

summary(gam_full)
#compareGLM(gam_full)

#concurvity(gam_full)
gam.check(gam_full)
```



```{r}
# Splitting the data
set.seed(1)

# using 70% of ds as training set and 30% as test set
sample = sample(c(TRUE, FALSE), nrow(final_df1), replace=TRUE, prob=c(0.7,0.3))
train  = final_df1[sample, ]
test   = final_df1[!sample, ]

# GAM

gam_full1 = gam(Song_Success~
                 s(Drums_Energy) +
                 s(Drums_Complexity) +
                 s(Variety_of_musical_instruments) +
                 s(Harmonic_Richness) +
                 s(Emotional_Intensity)+
                 s(Mixing_Quality),
               data = train,
               family = binomial,
               method = "REML",
               method.args = list(control = list(type =  "huber")))

test_prob = predict(gam_full1, newdata = test, type = "response")

# Creating ROC Curve Plot
library(pROC)
test_roc = roc(test$Song_Success ~ test_prob, plot = TRUE, print.auc = TRUE)

print(paste("GLM Area Under Curve:",test_roc$auc))
```


