---
title: "Hypothesis 1 Number of Previous Hits"
author: "Timur Sharifullin"
date: "2023-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(ggeffects)
library(mgcv)
```


*Hypothesis 1.*
The success of a given song is positively associated with the number of successful songs previously released by the artist, such that a higher number of previous successful songs in the artist's discography will increase the likelihood of the given song achieving success (becoming a hit).


# Uploading data
```{r}
final_df = read.csv("Clean_Dataset.csv")
final_df$Song_Success = factor(final_df$Song_Success, levels = c("none","hit"))
final_df1 = final_df[,c("hit_n","Song_Success")]
```

# Outliers
```{r}
library(outliers)
grubbs.test(filter(final_df1,hit_n<21)$hit_n)
dataset = filter(final_df1,hit_n<17)
nrow(dataset)
```

```{r}
library(table1)
library(flextable)
dataset1 = dataset
dataset1$hit_n = as.factor(dataset1$hit_n)
label(dataset1$hit_n) = "Number of Previous Hits"

dataset1$Song_Success = factor(dataset1$Song_Success,levels = c("hit", "none"), labels=c("Hit","Non-Hit"))

final_model_desc = table1(~ hit_n| Song_Success, data=dataset1)
final_model_desc

t1flex(final_model_desc) %>% 
  save_as_docx(path="hyp1.docx")
```


# GAM - Linear

```{r}
m_logit = glm(data = dataset, formula = Song_Success ~ hit_n,
              family = binomial(link = "logit"))

summary(m_logit)
```

## Linearity Assumption

```{r}
# Predict the probability (p) of song success
probabilities <- predict(m_logit, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "pos", "neg")

# Select only numeric predictors
mydata <- filter(dataset) %>% dplyr::select(hit_n)
predictors <- colnames(mydata)
# Bind the logit and tidying the data for plot

mydata <- mydata %>%
  mutate(logit = log(probabilities/(1-probabilities))) %>%
  gather(key = "predictors", value = "predictor.value", -logit)

ggplot(mydata, aes(logit, predictor.value))+
  geom_point(size = 2, alpha = 0.5) +
  geom_smooth(method = "loess") + 
  theme_bw() #+ 
  #facet_wrap(~predictors, scales = "free_y")
```


# GAM - Smooth

```{r}
m_logit1 = gam(data = dataset, formula = Song_Success ~ s(hit_n),
              family = binomial(link = "logit"),method = "REML")

summary(m_logit1)
```

## K-Basis

full convergence after 4 iterations.
k' = 9.00, edf = 6.32.

```{r}
gam.check(m_logit1)
```


# Comparison

```{r}
AIC(m_logit, m_logit1)
```

Smooth Term significantly lower AIC

```{r}
anova(m_logit, m_logit1, test = "Chisq")
```

Significantly better.

# Predicted Probabilities plot

```{r}
plot(ggpredict(m_logit))[[1]] + labs(title = NULL, y = "Predicted Probability of Hit", x ="Number of Previous Hits") + scale_y_continuous(breaks = seq(0,1,0.05))

ggpredict(m_logit) %>% as.data.frame()
```

```{r}
ggpredict(m_logit1) %>% as.data.frame()
```



